Active Learning from Blackbox to Timed Connectors

### 2016-04-17 shortpaper/paper.tex
.

%\subsection{Observation Table}
%\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
%hypothetical Mealy machines from the results of membership queries.

%Mealy machines consist of \emph{states} and \emph{transitions}.
%As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
%after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
%state of $s$ after executing $a$.
%However, under such notations, there are \emph{infinite} number of states, among which most are
%duplicate.

%States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
%\mathcal{I}^*$, we say the corresponding of states $s_1$ and $s_2$ are equivalent iff $\forall d\in
%\mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
%alternative way is to use a set of \emph{suffixes} to distinguish them approximately.
%\begin{definition}[$D$-Equivalence]
  %Provided with a set of suffixes $D\subset\mathcal{I}^+$, the corresponding states of
  %$s_1,s_2\in\mathcal{I}^*$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
  %iff $mq(s_1d) = mq(s_2d)$ for all $d\in D$.
%\end{definition}

>>>>

\subsection{Observation Table}
\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
hypothetical Mealy machines from the results of membership queries.

Mealy machines consist of \emph{states} and \emph{transitions}.
As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
state of $s$ after executing $a$.
However, under such notations, there are \emph{infinite} number of states, among which most are
duplicate.

States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
\mathcal{I}^*$, we say the corresponding of states $s_1$ and $s_2$ are equivalent iff $\forall d\in
\mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
alternative way is to use a set of \emph{suffixes} to distinguish them approximately.
\begin{definition}[$D$-Equivalence]
  Provided with a set of suffixes $D\subset\mathcal{I}^+$, the corresponding states of
  $s_1,s_2\in\mathcal{I}^*$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
  iff $mq(s_1d) = mq(s_2d)$ for all $d\in D$.
\end{definition}
